Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2022-11-08 paper/paper/SPIE/article.tex
[WIP]

>>>>

\subsection{Normalization}

Because of the exponential distribution of the eigenfeatures, normalization is
somewhat non-trivial, and a simple standardization or min-max normalization is
ineffective. We instead first apply a logarithm to all eigenfeatures, and then
test each classifier with un-normalized or min-max normalized versions of the
log-features. Baseline features are also tested with un-normalized and min-max
normalized versions, but without any log transform.
